\section{Thermal}
\label{ap:thermal}
The system require is for reliable operating at an ambient temperature of 105 degrees C.
Therefore, all sourced parts have a minimum operating temperature of 105 degrees.
Several components have been selected for 125 degree C or above operation to reliability, these are listed in following sections.

\subsection{Regulator Thermal Calculations}
\label{ap:regulator}
For reliable operation the regulator junction temperature must not exceed $\SI{125}{\degreeCelsius}$. 
The junction temperature is a function of ambient temperature and power dissipated, due to load current and voltage differential between supply and output.
$\theta J_A$ defines the device's ability dissipate heat.
Using a SOIC 8-Ld device, $\theta J_A = \SI{65}{\degreeCelsius}$.
\begin{align}
	PD_{max} &= \frac{T_{max} - T_{ambient}}{\theta J_A} \\ 
	\therefore PD_{max} &= \frac{125-105}{ 65} \nonumber \\
		&= \SI{317.46}{\milli\watt} \nonumber
\end{align}

\begin{align}
	PD_{operating} &= (V_{in} - V_{out})\times V_{out} \\
	\therefore PD_{worst case} &= (6-5)\times 200 \nonumber \\
		&= \SI{200}{\milli\watt} \nonumber
\end{align}

Hence $PD_{worst case} < PD_{max} \therefore$ device is suitable.
Substituting in $PD_{max}$ and rearranging shows the maximum continuous supply rail voltage is $\SI{6.585}{\volt}$ giving a limited safety margin.
If the worst case operating current is used, the supply rail voltage could go slightly higher.
Note that $V_{in}$ max is $\SI{26}{\volt}$.

\subsection{Op-Amp Thermal Calculations}
\label{ap:amplifier}
Power dissipation is a function of the difference between supply voltage to output voltage, output voltage difference to ground (for single supply devices) and the output current.
At low frequencies the RC filter presents the high input impedance MCU ADC input to the op-amp output.
Thus, the load is high impedance and little current is consumed.
At high frequencies, the op-amp output is $\SI{560}{\ohm}$ and current is increased.
However, noise signals are expected to be lower in amplitude than the signal, and thus the overall current consumption will be within an estimated $\pm \SI{2}{\milli\ampere}$.
Additionally the worst case quiescent current is $\SI{70}{\micro\ampere}$.
With a 5V supply and low current power dissipation is minimal, there is a comfortable margin between the ambient temperature of $\SI{105}{\degreeCelsius}$, the junction operating temperature of $\SI{125}{\degreeCelsius}$, and the device absolute maximum of $\SI{150}{\degreeCelsius}$.

